R5R

### 2020-08-21 r-package/tests_marcus/tests r5r.Rmd
Fixed travel distance in detailed_itineraries. Converted units from seconds and millimetres to minutes and meters.

```{r setup, include=FALSE}
options(java.parameters = "-Xmx8G")
knitr::opts_chunk$set(echo = TRUE)
# library("r5r")
library("tidyverse")
library("sf")
library("tmap")
library("mapproj")
library("lubridate")
```

@@

```{r}
r5r_core <- setup_r5(system.file("extdata", package = "r5r"), verbose = FALSE)
```

@@

```{r}
paths_df %>%
  ggplot() +
  geom_sf(data=street_net$edges, colour="grey85", aes(geometry=geometry)) +
  geom_sf(aes(geometry=geometry, colour=mode)) +
  facet_wrap(~option)
```

```{r}
points <- read_csv(system.file("extdata/poa_hexgrid.csv", package = "r5r"))
```

>>>>

```{r setup, include=FALSE}
options(java.parameters = "-Xmx8G")
knitr::opts_chunk$set(echo = TRUE)
# library("r5r")
library("tidyverse")
library("sf")
library("tmap")
library("mapproj")
library("lubridate")
library("purrr")
```

@@

```{r include=FALSE}
r5r_core <- setup_r5(system.file("extdata", package = "r5r"), verbose = FALSE)
```

@@

```{r}
paths_df %>%
  ggplot() +
  geom_sf(data=street_net$edges, colour="grey85", aes(geometry=geometry)) +
  geom_sf(aes(geometry=geometry, colour=mode)) +
  facet_wrap(~option)
```
```{r}

```{r}
paths_df %>%
  mutate(dist_m = distance, dist_geo = st_length(geometry)) %>% View()

  mutate(dist_sum = map_dbl(route, function(txt) {
           txt_list <- str_split(txt, pattern = " ", simplify = TRUE)
           num_list = as.numeric(txt_list)
           return(sum(num_list))
         }))
```

```{r}
paths_df %>% st_write("/Users/marcussaraiva/paths3.shp")
street_net$edges %>% st_write("/Users/marcussaraiva/streets.shp")
```

```{r}
points <- read_csv(system.file("extdata/poa_hexgrid.csv", package = "r5r"))
poi <- read_csv(system.file("extdata/poa_points_of_interest.csv", package = "r5r"))
```
